---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sqlqueries

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/JakubBujnowicz/sqlqueries/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JakubBujnowicz/sqlqueries/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/JakubBujnowicz/sqlqueries/graph/badge.svg)](https://app.codecov.io/gh/JakubBujnowicz/sqlqueries)
[![CRAN status](https://www.r-pkg.org/badges/version/sqlqueries)](https://CRAN.R-project.org/package=sqlqueries)
<!-- badges: end -->

The goal of **sqlqueries** is to build SQL queries programmatically in R
using composable functions — no string interpolation, messy concatenation,
or fighting with code formatting.

Writing SQL inside R code usually means embedding long strings with
`paste()` calls, line breaks, and lost syntax highlighting.
**sqlqueries** solves this by providing a clean, functional interface
where each clause is a separate function call. The result is formatted,
readable SQL that is easy to compose, modify, and maintain.


## Installation

The package is not yet on CRAN, but you can install the development
version from GitHub:

``` r
# pak
pak::pak("JakubBujnowicz/sqlqueries")

# or devtools
devtools::install_github("JakubBujnowicz/sqlqueries")
```

## Example

```{r example}
library(sqlqueries)

# Build a query by composing clauses
query <- sql(
    select("Species", "Sepal.Length", "Sepal.Width"),
    from("iris"),
    where("Species = 'setosa'"),
    order_by(vars(-Sepal.Length))
)

query
```


## Further reading

See the package documentation for a full list of functions:

``` r
help(package = "sqlqueries")
```
